---
title: "Cul Dat"
author: "Sigurd Fyhn Sørensen"
date: "2022-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(tidyverse)
library(rstanarm)
```

## What drives the stock market?
1) the government and its legislation,
2) international geopolitics/international transactions, 
3) supply and demand 
4) speculation and expectation


### My focus:

\- **Crypto Currency:**
  \- Can google trends drive/explain crypto prices?
  
Steps: 
1) Scrape cryptocurrency data using my script. 
2) Get google search historic from google trends. 
3) Apply a statisical analysis pipeline. 



##### For fun simulation of what data could look like. 

```{r}
n = 5e2

percentage_increase <- rnorm(n, mean = 0.2, sd = 3)

for (i in (1:n)){
  if (i == 1){
    crypto_price <- 80
  }
  else{
    crypto_price[i] <- crypto_price[i-1] + crypto_price[i-1]* (percentage_increase[i]/100)
  }
  
}

plot(crypto_price, type = "l", xlab = "Weeks since coin start")
```


```{r}
e <- abs(rnorm(n,mean=0,sd=1))

alpha <- 10
beta <- 0.0001
theta <- 0.9
crypto_search <- 0
for(i in 2:length(e)){
  crypto_search[i] <- abs(alpha+beta*i+theta*crypto_search[i-1]+e[i])
}

plot(crypto_search, type = "l", xlab = "Weeks since coin start")
```


```{r}
crypto_price <- crypto_price + crypto_seach * 2


df <- tibble(crypto_price, crypto_search, n = 1:n)
```


```{r}

ggplot(df) + geom_line(aes(y = crypto_price, x = n, col = "red")) + 
  geom_line(aes(x = n , y = crypto_seach))
```


```{r}
print(ccf(crypto_price, crypto_seach))
```

