---
title: "day2 Kings"
author: "Sigurd Sørensen"
date: '2022-08-31'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

## 1
Create a spreadsheet listing the names of Danish monarchs with their birth- and death-date and start and end year of reign. Make it *tidy*! They should be sortable by year of birth. Suitable source websites are here and here, but you can also use another source, provided you reference it. (Group collaboration is expected and welcome. Remember to attach this spreadsheet to Brightspace submission)
Does OpenRefine alter the raw data during sorting and filtering?
  - You never change the raw data but it saves a log of each new itteration and all its changes. (But I like to work in R xD xD xD )

```{r}
kings <- c("Margrethe 2.
Siden 1972

Frederik 9.
1947 - 1972

Christian 10.
1912-1947

Frederik 8.
1906-1912

Christian 9.
1863-1906

Frederik 7.
1848-1863

Christian 8.
1839-1848

Frederik 6.
1808-1839

Christian 7.
1766-1808

Frederik 5.
1746-1766

Christian 6.
1730-1746

Frederik 4.
1699-1730

Christian 5.
1670-1699

Frederik 3.
1648-1670

Christian 4.
1588-1648

Frederik 2.
1559-1588

Christian 3.
1536-1559

Interregnum
1533-1536

Frederik 1.
1523-1533

Christian 2.
1513-1523

Hans
1482-1513

Christian 1.
1448-1481

Christoffer 3. af Bayern
1440-1448

Erik 7. af Pommern
1396-1439

Margrete 1.
1387-1396

Oluf 2.
1375-1387

Valdemar 4. Atterdag
1340-1375

Interregnum
1332-1340

Christoffer 2.
1329-1332

Valdemar 3.
1326-1329

Christoffer 2.
1319-1326

Erik 6. Menved
1286-1319

Erik 5. Klipping
1259-1286

Christoffer 1.
1252-1259

Abel
1250-1252

Erik 4. Plovpenning
1241-1250

Valdemar 2. Sejr
1202-1241

Knud 4.
1182-1202

Valdemar 1. den Store
1157-1182

Svend 3., Knud 3., Valdemar 1.
1146-1157

Erik 3. Lam
1137-1146

Erik 2. Emune
1134-1137

Niels
1104-1134

Erik 1. Ejegod
1095-1103

Oluf 1. Hunger
1086-1095

Knud 2. den Hellige
1080-1086

Harald 3. Hen
1074-1080

Svend 2. Estridsen
1047-1074

Magnus den Gode
1042-1047

Hardeknud
1035-1042

Knud 1. den Store
1018-1035

Harald 2.
1014-1018

Svend 1. Tveskæg
D. 1014

Harald 1. Blåtand
D. senest 987

Gorm den Gamle.
936, d. ca. 958")


kings <- str_split(kings,pattern = "\n") 
```

```{r}
df_kings <- data.frame(Names = kings[[1]][seq(from = 1, to = length(kings[[1]]), by = 3 )], Year = kings[[1]][seq(from = 2, to = length(kings[[1]]), by = 3 )])
df_kings
```

## 2
Fix the interviews dataset in OpenRefine enough to answer this question: "Which two months are reported as the most water-deprived/driest by the interviewed farmer households?"
```{r}
df_random <- read_csv("SAFI_openrefine.csv")

df_random_long <- df_random %>% 
  separate_rows(months_no_water, sep = ";")

df_random_long <- df_random_long %>% 
  mutate(months_no_water = gsub('[[:punct:]]',"", df_random_long$months_no_water)) %>% 
  mutate(months_no_water = gsub('[[:space:]]',"", df_random_long$months_no_water)) 

unique(df_random_long$months_no_water) #Sanity check to see if all is tidy.
```


```{r}
df_random_long %>% 
  filter(months_no_water != "NULL") %>% 
  count(months_no_water) %>% 
  arrange(desc(n))
```
October and September is the two months reported the most times as being without water. 

## 3
Real-Data-Challenge: What are the 10 most frequent occupations (erhverv) among unmarried men and women in 1801 Aarhus? (hint: some expert judgement interpretation is necessary, look at the HISCO classification "Historical International Standard of Classification of Occupations" on Dataverse if ambitious)

```{r}
df_aarhus <- read_csv("https://raw.githubusercontent.com/aarhusstadsarkiv/datasets/master/censuses/1801/census-1801-normalized.csv")

df_aarhus %>% 
  filter(!is.na(erhverv)) %>% 
  count(erhverv)
```
The data is still super messy so let us try and clean it up a bit. 

```{r}
df_aarhus <- df_aarhus %>% 
  filter(!is.na(erhverv))

df_aarhus %>% 
  mutate(erhverv = str_to_lower(gsub('[[:punct:]]', '', df_aarhus$erhverv))) %>%
  count(erhverv) %>% 
  filter(n > 3) %>% 
  arrange(desc(n))

```

We could now stem all words and use a danish stopword list to clean it even further. That requires a library and a stopword list that works with the danish languages. 

